Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
Repaired broken reference (thanks Paul)

	\subsection{Existence condition}
		As in the synchronous case, the problem of existence of the first periodic DIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

>>>>

	\subsection{Existence condition}
  \label{sct:FPDITexist}
		As in the synchronous case, the problem of existence of the first periodic DIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]
